Proof of uniform convergence for a cell-centered AP discretization of the hyperbolic heat equation on general meshes

### 2015-03-20 Corrected_version.tex
Corrections u->p

Using the definitions of $u_j$ \eqref{schemadiff3}, the $L^2$ norm of $S_h = (S_{j+\frac12})_{j\in\mathbb{Z}}$ is related to the $L^2$ norm of $\frac{d}{dt}u_j$. Using once again the proposition \ref{pro:H1}, one finds out that 

@@

\begin{lemma}\label{pro:H1}
The bound $
\sqrt{ \sum_j \Delta x_j (\frac{d}{dt}u_j)^2(t) }
\leq \sigma^{-1}\|p_0\|_{H^2(\mathbb{R})}$
 holds at any time.\end{lemma}

>>>>

Using the definitions of $u_j$ \eqref{schemadiff3}, $S_{j+\frac12}$ can be written in terms of $\frac{d}{dt}p_j$ and $\frac{d}{dt}p_{j+1}$
S_{j+\frac12} = \frac{\eps}{2} \bigg( \frac{\Delta x_{j} }{\Delta x_{j+\frac12} }\frac{d}{dt}p_j - \frac{\Delta x_{j+1} }{\Delta x_{j+\frac12} }\frac{d}{dt}p_{j+1} \bigg).
Using once again the proposition \ref{pro:H1}, one finds out that $S_h = (S_{j+\frac12})_{j\in\mathbb{Z}}$ satisfies

@@

\begin{lemma}\label{pro:H1}
The bound $
\sqrt{ \sum_j \Delta x_j (\frac{d}{dt}p_j)^2(t) }
\leq \sigma^{-1}\|p_0\|_{H^2(\mathbb{R})}$
 holds at any time.\end{lemma}
